Exploring Feature Engineering

### 2019-03-08 Scripts/evaluating_correlations.Rmd
added code for new correlation figures

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)

@@

>>>>

```{r}
library(GenomicRanges)
library(caret)
library(data.table)
library(gbm)
library(randomForest)
library(glmnet)
library(pROC)
library(plyr)
library(dplyr)
library(ggplot2)
library(DMwR)
library(gridExtra)
library(pROC)
library(ROCR)
#library(leaps)
library(cluster)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)

@@

## Using corrplot function

### GM12878

#### 10kb

cormat <- cor(binswtad, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

#### 25kb

train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")

cormat <- cor(binswtad, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

#### 50kb

train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")

cormat <- cor(binswtad, method = "spearman")

corrplot(cormat, 
         type="lower", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

#### 100kb

train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")

cormat <- cor(binswtad, method = "spearman")

corrplot(cormat, 
         type="lower", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

### K562

#### 10kb

cormat <- cor(binswtad, method = "spearman")
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .3,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

#### 25kb

train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")

cormat <- cor(binswtad, method = "spearman")
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .3,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

#### 50kb

train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")

cormat <- cor(binswtad, method = "spearman")
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]

corrplot(cormat, 
         type="lower", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .3,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

#### 100kb

train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")

cormat <- cor(binswtad, method = "spearman")
#remove Znf274 columns
#(no counts in flanked tad regions)
#therefore the corelation will be NA with all other features
cormat <- cormat[-which(rownames(cormat) == "Znf274"), -which(colnames(cormat) == "Znf274")]

corrplot(cormat, 
         type="lower", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .3,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))
